Unveiling the 2022 Iran Protests: Insights from HRANA's Dataset

### 2024-04-12 paper/paper.qmd
Typo fixed

On 16 September 2022, Mahsa Amini, a 22-year-old woman died under police custody in Iran. Reportedly, she was arrested because of not wearing her hijab (headscarf) properly. While officials claimed she died from a heart attack, her family disputed this. CCTV footage showed her collapsing at a "re-education" center. Iranians, especially on social media, demanded justice using hash tags like #MahsaAmini. The incident highlighted concerns about women's rights and government oppression in Iran, drawing international attention and calls for accountability [@CNN2022].

@@

The graphs and tables in this paper were created in R Studio using R [@citeR] and the analysis in a Quarto document. The analysis was conducted with the use of the `ggplot` [@ggplotRef], `tiddyverse` [@tidyverseRef], `knitr` [@knitrRef], `readr` [@readRef], `kableExtra` [@kableextraRef], `janitor` [@janitorRef], `tibble` [@tibbleRef], `arrow` [@arrow] and `dyplr` [@dplRef ] packages.

@@

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Dataset Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

The @fig-arrested illustrates the dynamics of arrests during the 2022 Iran protests over a period of 158 days. The x-axis represents the timeline, spanning from the start to the end of the protest period, while the y-axis denotes the number of arrests.

The @fig-arrested features two lines: one depicting the cumulative count of individuals arrested (denoted by "Individuals Arrested" in black), and the other showing the cumulative count of students arrested (denoted by "Students Arrested" in dark gray). The plot provides a visual comparison between the total number of arrests and the subset of arrests involving students, offering insights into the extent of student involvement in the protests and the overall scale of government crackdowns during the observed period.

@@

The @fig-total-arrested illustrates the stark difference between the total number of individuals arrested and the number of students among them. The dark gray bars represent the total number of arrested individuals, while the light gray bars specifically denote the total number of students arrested. This visualization effectively highlights the proportion of students within the broader context of arrests during the protests.

@@

```{r}
#| label: fig-total-arrested
#| include: true
#| fig-cap: Total of Individuals and Student Who Were Arrested in 158 Days
#| warning: false
#| message: false
#| echo: false

@@

# Create the bar plot
bar_plot <- ggplot(arrest_data, aes(x = Category, y = Count, fill = Category)) +
  geom_bar(stat = "identity", fill = c("darkgray", "lightgray")) +
  labs(x = "Category", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") +
  geom_text(aes(label = Count), vjust = -0.3, size = 3.5)

@@

The @fig-protesters-killed shows a chronological sequence of dates and the corresponding total number of protesters killed during the 158-day protest period. The figure reveals an overall upward trend in the number of protesters killed, with occasional accelerations and fluctuations. Inflection points indicate significant junctures in the protest movement. The plot highlights the human cost of political unrest and underscores the importance of monitoring and documenting such events to promote accountability and justice.

@@

The dark gray area in the @fig-involved-cities-and-uni shows the total number of cities that participated in the protests and the light gray area represents the cumulative count of universities involved. The @fig-involved-cities-and-uni demonstrates that there was persistent growth in the involvement of both cities and universities throughout the 158-day period, which underscores the widespread nature of the protest movement. The upward trend in the cumulative counts of both cities and universities suggests ongoing mobilization and participation across diverse geographical locations and academic institutions.

>>>>

On 16 September 2022, Mahsa Amini, a 22-year-old woman died under police custody in Iran. Reportedly, she was arrested because of not wearing her hijab (headscarf) properly. While officials claimed she died from a heart attack, her family disputed this. CCTV footage showed her collapsing at a "re-education" center. Iranians, especially on social media, demanded justice using hashtags like #MahsaAmini. The incident highlighted concerns about women's rights and government oppression in Iran, drawing international attention and calls for accountability [@CNN2022].

@@

The graphs and tables in this paper were created in R Studio using R [@citeR] and the analysis in a Quarto document. The analysis was conducted with the use of the `ggplot` [@ggplotRef], `tiddyverse` [@tidyverseRef], `knitr` [@knitrRef], `readr` [@readRef], `kableExtra` [@kableextraRef], `janitor` [@janitorRef], `tibble` [@tibbleRef], `arrow` [@arrow] and `dyplr` [@dplRef] packages.

@@

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Observation Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

@fig-arrested illustrates the dynamics of arrests during the 2022 Iran protests over a period of 158 days. The x-axis represents the timeline, spanning from the start to the end of the protest period, while the y-axis denotes the number of arrests.

@fig-arrested features two lines: one depicting the cumulative count of individuals arrested (denoted by "Individuals Arrested" in black), and the other showing the cumulative count of students arrested (denoted by "Students Arrested" in dark gray). The plot provides a visual comparison between the total number of arrests and the subset of arrests involving students, offering insights into the extent of student involvement in the protests and the overall scale of government crackdowns during the observed period.

@@

@fig-total-arrested illustrates the stark difference between the total number of individuals arrested and the number of students among them. The dark gray bars represent the total number of arrested individuals, while the light gray bars specifically denote the total number of students arrested. This visualization effectively highlights the proportion of students within the broader context of arrests during the protests.

@@

```{r}
#| label: fig-total-arrested
#| include: true
#| fig-cap: Total of Individuals and Students Who Were Arrested in 158 Days
#| warning: false
#| message: false
#| echo: false

@@

# Create the bar plot
bar_plot <- ggplot(arrest_data, aes(x = Category, y = Count, fill = Category)) +
  geom_bar(stat = "identity", fill = c("darkgray", "lightgray")) +
  labs(x = "Category", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") +2
  geom_text(aes(label = Count), vjust = -0.3, size = 3.5)

@@

@fig-protesters-killed shows a chronological sequence of dates and the corresponding total number of protesters killed during the 158-day protest period. The figure reveals an overall upward trend in the number of protesters killed, with occasional accelerations and fluctuations. Inflection points indicate significant junctures in the protest movement. The plot highlights the human cost of political unrest and underscores the importance of monitoring and documenting such events to promote accountability and justice.

@@

The dark gray area in @fig-involved-cities-and-uni shows the total number of cities that participated in the protests and the light gray area represents the cumulative count of universities involved. @fig-involved-cities-and-uni demonstrates that there was persistent growth in the involvement of both cities and universities throughout the 158-day period, which underscores the widespread nature of the protest movement. The upward trend in the cumulative counts of both cities and universities suggests ongoing mobilization and participation across diverse geographical locations and academic institutions.
